A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-10-09 paper/paper.tex
a first conclusion

\paragraph{TODO: Monte Carlo optimization.}
Some text snippets that might be pertinent:
Monte-Carlo simulation can be used to update the agent’s belief state
\cite{silver2010monte}.
Monte-Carlo simulation provides a simple method for evaluating
a state s.
In any MDP, there is at least one optimal policy matrix that
achieves the optimal value function???
The simulator is used to generate sequences of states, observations and rewards. These simulations are used to update the value function, without ever looking inside the black box describing the model’s dynamics. In addition, Monte-Carlo methods have a sample complexity that is determined only by the underlying difficulty of the POMDP, rather than the size of the state space or observation space.
Monte-Carlo simulation can be turned into a simple control algorithm by evaluating all legal actions and selecting the action with highest evaluation [15]. Monte-Carlo simulation can be extended to partially observable MDPs.
In these challenging POMDPs, Monte-Carlo simulation provides an effective mechanism both for tree search and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible.
Link this to experience sampling in the hippocampus.

@@

\section{Conclusion}
What single brain function could be most important for existence and survival of the species?
Estimating quantities that depend on how features of an agent’s environment are expected to unfold over the future.
From the perspective of the human condition, it remains unclear what the nature and purpose of a domain-overarching computational mechanism implemented in the high association cortex could be to warriant the high energetic costs.
MDP conceptualize control of the environment.
Obtain reward and avoid pain by adaptive behavior.
How representations of past and future are integrated into
action choice in the present context.
The idealized computational framework explains previous observations about the
DMN in a simple in conception but non-trivially links
together disparate functional hypotheses in the DMN literature.
The default brain function may be reducible to a small number
of well-defined equations.
biological plausibility of dynamic optimization in
optimal substructure
mathematical formalism; statistical solution; adaptive fitness
to optimize the organism's fate; contribute to human survival and
creativity.
; formalize and predict; offer statistical control on the brain's default function/operations
stochastic modelling
At the least, we propose an alternative vocabulary to
describe and discuss neuroscientific studies on the DMN.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of RL systems. This makes proposed machine-learning
approach to DMN function not only practically computable but
also neuroscientifically falsifiable.
%
The DMN can be viewed as a smoothing kernel extending
from the relatively recent past to the relatively close future
that constantly estimates complex non-linear gain functions.
-> This is why neuroimaging research revealed activity increases in the DMN
when 
-> This may be why perfect memory has been evolutionarily de-selected,
although it is provably feasible by the neurobiological hardware in humans

>>>>

\paragraph{TODO: Monte Carlo optimization.}
Some text snippets that might be pertinent:
Monte-Carlo simulation can be used to update the agent’s belief state
\cite{silver2010monte}.
Monte-Carlo simulation provides a simple method for evaluating
a state s.
In any MDP, there is at least one optimal policy matrix that
achieves the optimal value function???
The simulator is used to generate sequences of states, observations and rewards. These simulations are used to update the value function, without ever looking inside the black box describing the model’s dynamics. In addition, Monte-Carlo methods have a sample complexity that is determined only by the underlying difficulty of the POMDP, rather than the size of the state space or observation space.
Monte-Carlo simulation can be turned into a simple control algorithm by evaluating all legal actions and selecting the action with highest evaluation [15]. Monte-Carlo simulation can be extended to partially observable MDPs.
In these challenging POMDPs, Monte-Carlo simulation provides an effective mechanism both for tree search and for belief state updates, breaking the curse of dimensionality and allowing much greater scalability than has previously been possible.
Link this to experience sampling in the hippocampus.
Much recent work points to Monte Carlo or stochastic sampling– based approximations as a unifying framework for understanding how Bayesian inference may work practically across all these levels, in minds, brains, and machines.

@@

\section{Conclusion}
What brain function could be important enough
for the existence and survival of the human species
to warrant constant, high energy costs?
MDPs provide an attractive
computational model how the human association cortex
might implement high-level control of the environment to
optimize the organism's fate by obtaining reward and avoiding pain.
This idealized process model explains
a number of previous experimental observations in the
DMN literature by a simple but non-trivial concept.
%
Viewed as a MDP, behavior unfolds by integrating across past
and future experience to guide action choice in the present context.
This account is more compatible with the DMN's involvement across
autobiographical memory retrieval,
abstract reasoning based on internally generated scenes,
and self-projection into the expected future.
MDPs provide a mathematical formalism how
optimal substructure can be recursively exploited
when contemplating nested decisions.
Algorithmic gains by injecting stochasticity in past
behavior and outcomes may plausibilize why
very accurate memories have been evolutionarily de-selected
and why human creativity might be adaptive.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of RL systems. This makes the proposed machine-learning
approach to DMN function not only practically computable but
also neuroscientifically falsifiable.
At the least, we propose an alternative vocabulary to
describe and discuss neuroscientific studies in DMN research.
%
Ultimately,
the DMN can be viewed as a smoothing kernel extending
from the relatively recent past to the relatively close future
to constantly compute complex gain opportunities in the world.
